---
title: "Coronavirus Beliefs Analysis"
author: "Eliana"
date: "2026-03-12"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(dplyr)
library(readr)
library(ggplot2)

options(scipen=999)

d_coronavirus <- read_csv('../Data/life-under-lockdown-wave2-extract.csv')
```

# Hypotheses

H1 Gender is associated with number of conspiracy beliefs about coronavirus
H2 Age is associated with number of consipiracy beliefs about coronavirus
H3 Reliance on Facebook for information about coronavirus is associated with number of conspiracy beliefs about coronavirus

# Findings
## Hypothesis 1
```{r}
d_coronavirus %>%
  group_by(
    gender
  ) %>%
  summarise(
    n = n(),
    Mdn = median(beliefs),
    M = mean(beliefs),
    SD = sd(beliefs)
  )
```

```{r}
d_coronavirus %>%
  filter(gender != 'In another way') %>%
  t.test(
    beliefs ~ gender,
    data = .
  )
```

Males in the sample believed in slightly more conspiracy theories than females in the sample, but this was not statistically significant, t(494.31) = -1.201, p = .230.

## Hypothesis 2
```{r}
d_coronavirus %>%
  ggplot(
    aes(x = age, y = beliefs)
  ) +
  geom_jitter()
```

```{r}
d_coronavirus %>%
  cor.test(
    ~ beliefs + age,
    data = .
  )
```

Age is negatively associated with number of consipiracy beliefs about coronavirus, r(498) = -.24, p<.001

## Hypothesis 3
```{r}
knowledge_level <- c(
  'Nothing at all',
  'Not very much',
  'A fair amount',
  'A great deal'
)

d_coronavirus <- d_coronavirus %>%
  mutate(
    know_facebook = know_facebook %>%
      ordered(
        levels = knowledge_level
      )
  )

d_coronavirus %>%
  ggplot(
    aes(x = know_facebook , y = beliefs)
  ) +
  geom_violin()
```

```{r}
d_coronavirus <- d_coronavirus %>%
  mutate(
    know_facebook_coded = know_facebook %>%
      as.numeric()
  )

d_coronavirus %>%
  cor.test(
    ~ beliefs + know_facebook_coded,
    data = .,
    method = 'spearman'
  )
```

Reliance on Facebook for information about coronavirus is positively associated with number of conspiracy beliefs about coronavirus, rs(498) = .23, p < .001.